---
title: "canClimateData"
author: "Alex Chubaty"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    df_print: paged
    keep_md: yes
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE, warning = FALSE, results = "hold")

if (!require("Require", quietly = TRUE)) {
  install.packages("Require")
  library(Require)
}
Require("SpaDES.core", require = FALSE, upgrade = FALSE)
Require(c("knitr", "kableExtra", "magrittr"))
```

# Overview

Prepare Canadian historic and projected climate data for use with LandR.CS and fireSense.

Currently supports study areas in AB, BC, SK, MB, ON, QC, NT, and YT, for some CMIP6 climate scenarios (see below).

# Parameters

Provide a summary of user-visible parameters.

```{r moduleParams, eval = TRUE, echo = FALSE, message = FALSE, warning = FALSE}
df_params <- SpaDES.core::moduleParams("canClimateData", "..")
knitr::kable(df_params)
```

# Events

This module consists of a single `init` event that performs all the data preparation.

# Data dependencies

## Input data

```{r moduleInputs, eval = TRUE, echo = FALSE, message = FALSE, warning = FALSE}
df_inputs <- SpaDES.core::moduleInputs("canClimateData", "..")
knitr::kable(df_inputs)
```

### Historic and projected climate data

### Prerequisites

1. DEM from GEOTOPO15 product
2. Climate data using [ClimateNA](https://climatena.ca) with projected climate scenario(s).

### Available data sets

```{r climateStudyAreas, eval = TRUE, echo = FALSE, message = FALSE, warning = FALSE}
#csv <- file.path("modules", "canClimateData", "data", "climateDataURLs.csv")
csv <- file.path("data", "climateDataURLs.csv")
df_climate <- read.csv(csv, stringsAsFactors = FALSE)
df_climate <- subset(df_climate, select = c("studyArea", "GCM", "SSP")) |> na.omit() |> unique()
df_climate <- df_climate[order(df_climate$studyArea, df_climate$GCM, df_climate$SSP), ]
g <- which(as.integer(as.factor(df_climate$studyArea)) %% 2 == 0) ## alternate by group
knitr::kable(df_climate, row.names = FALSE) %>% 
  kable_styling(full_width = FALSE) %>% 
  row_spec(g, background = "#f0f0f0")
```

### Additional data sets

Other study areas and/or climate scenarios can be added by making suitable `.zip` archives available via Google Drive and updating the `climateDataURLs.csv` file accordingly.

**NOTE:** the following naming conventions should be used for the `.zip` archives:

```{r naming, eval = TRUE, echo = FALSE, message = FALSE, warning = FALSE}
df_znames <- data.frame(
  "Description" = c("Historic normals: 1951-1980Y and 1981_2010Y",
                    "Historic monthly: 1991-2020",
                    "Projected annual: 2011-2100",
                    "Projected monthly: 2011-2100"),
  "Archive Filename" = c("studyAreaNameLong_normals.zip",
                         "studyAreaNameLong.zip",
                         "climateGCM_climateSSP_studyAreaNameLong_annual,zip",
                         "climateGCM_climateSSP_studyAreaNameLong,zip")
)
knitr::kable(df_znames)
```

## Output data

Description of the module outputs.

```{r moduleOutputs, eval = TRUE, echo = FALSE, message = FALSE, warning = FALSE}
df_outputs <- SpaDES.core::moduleOutputs("canClimateData", "..")
knitr::kable(df_outputs)
```

# Links to other modules

Originally developed to provide inputs to `gmcsDataPrep` (for use with climate-sensitive LandR Biomass projections; see `Biomass_core`) and the `fireSense` suite of modules.
